Size-differentiated Export \add{Flux} in Different Dynamical Regimes in the Ocean

### 2020-07-06 size_differentiated_export.tex
Updates from Overleaf

	We  rely on a submesoscale-resolving, non-hydrostatic  ocean model to simulate the dynamics in the upper few hundred meters of the ocean. 
	The dynamical model is coupled with a particle-tracking module to model the advection of particles by fluid flow, while neglecting the effects of particle inertia and drag on their advection. In addition, the particles sink with a range of sinking velocities (between 0.025--5 m day$^{-1}$) \add{that is based on the range of vertical currents modeled in this region. We aim to address the transitional regime of the particle sinking velocity spectrum, where both advection and sinking speeds have similar order of magnitudes. A similar study with sinking tracers  showed the influence of the flow \citep{taylor2020influence}, but the use of particles enables a characterization of export associated with each sinking  class of particles. }
%	This transitional regime will vary depending on the local dynamics; in strong frontal regions such as western boundary currents, vertical currents can $\mathcal{O}$(100 m/day), but the region modeled in this study has weak submesoscale activity and vertical velocities, particularly in summer.}

>>>>

	We  rely on a submesoscale-resolving, non-hydrostatic  ocean model to simulate the dynamics in the upper few hundred meters of the ocean. 
	The dynamical model is coupled with a particle-tracking module to model the advection of particles by fluid flow, while neglecting the effects of particle inertia and drag on their advection. In addition, the particles sink with a range of sinking velocities (between 0.025--5 m day$^{-1}$) \add{that is based on the range of vertical currents modeled in this region. We aim to address the transitional regime of the particle sinking velocity spectrum, where both advection and sinking speeds have similar order of magnitudes. A similar study with sinking tracers  showed the influence of the flow }\citep{taylor2020influence}\add{, but the use of particles enables a characterization of export associated with each sinking  class of particles. }
%	This transitional regime will vary depending on the local dynamics; in strong frontal regions such as western boundary currents, vertical currents can $\mathcal{O}$(100 m/day), but the region modeled in this study has weak submesoscale activity and vertical velocities, particularly in summer.}
